---
title: "Consultations paper tables (excluding baseline characteristics tables)"
author: "Yamina Boukari / Claire Zhang"
date: "`r Sys.Date()`"
output: 
  word_document:
    reference_docx: reference_table_doc.docx
---

```{r setup, include=FALSE, quiet = TRUE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Load packages ----
if (!require('pacman')) install.packages('pacman')
pacman::p_load(tidyverse,lubridate, Hmisc, epitools, data.table, epiR, flextable,
               gtsummary)

# Set working directory ----
setwd("filepath")

```

## Table SX: Crude consultations rates 2015-2020 by migration status and migration certainty

```{r echo=FALSE, message = FALSE, quiet=TRUE, warning=FALSE}

# Load packages ----
if (!require('pacman')) install.packages('pacman')
pacman::p_load(tidyverse,lubridate, Hmisc, epitools, data.table, epiR, flextable,
               gtsummary)

# Set working directory ----
setwd("filepath")
# Load files
load(file = "filepath")
load(file = "filepath")
load(file = "filepath")
load(file = "filepath")
# Format data ready for table
IR_allpatients_overall_migstatus_studyyear$studyyear <- as.factor(IR_allpatients_overall_migstatus_studyyear$studyyear)
IR_allpatients_overall_migcertainty_studyyear$studyyear <- as.factor(IR_allpatients_overall_migcertainty_studyyear$studyyear)
IR_allpatients_overall_migcertainty_studyyear <- IR_allpatients_overall_migcertainty_studyyear %>%
  filter(migcertainty %in% c('Definite', 'Probable')) %>%
  rename(migrant_status = migcertainty)

IR_allpatients_overall_migstatus <- IR_allpatients_overall_migstatus %>%
  mutate(studyyear = '2015-2019') %>%
  relocate(studyyear)
IR_allpatients_overall_migcertainty <- IR_allpatients_overall_migcertainty %>%
  mutate(studyyear = '2015-2019') %>%
  relocate(studyyear) %>% 
  filter(migcertainty %in% c('Definite', 'Probable')) %>%
  rename(migrant_status = migcertainty)
IR_allpatients_overall_migstatus$studyyear <- as.factor(IR_allpatients_overall_migstatus$studyyear)
IR_allpatients_overall_migcertainty$studyyear <- as.factor(IR_allpatients_overall_migcertainty$studyyear)


IRs_annual <- bind_rows(IR_allpatients_overall_migstatus, IR_allpatients_overall_migstatus_studyyear,
                        IR_allpatients_overall_migcertainty, IR_allpatients_overall_migcertainty_studyyear) %>%
  arrange(studyyear) %>%
  dplyr::select(c(studyyear, migrant_status, ir_ci)) %>%
  tidyr::pivot_wider(names_from = migrant_status, values_from = ir_ci) 

# Make table
IRs_annual <- flextable(IRs_annual)
IRs_annual <- flextable::align(IRs_annual, align = 'center', part = 'header')%>%
  flextable::set_table_properties(layout = 'autofit')

IRs_annual
```


## Table SX: Crude consultations rates before and during the pandemic by migration status and migration certainty

```{r echo=FALSE, message = FALSE, quiet=TRUE, warning=FALSE}

# Load packages ----
if (!require('pacman')) install.packages('pacman')
pacman::p_load(tidyverse,lubridate, Hmisc, epitools, data.table, epiR, flextable,
               gtsummary)

# Set working directory ----
setwd("filepath")
load(file = "filepath")

IRs_pandemic <- flextable(IRs_pandemic_combined)
IRs_pandemic <- flextable::align(IRs_pandemic, align = 'center', part = 'header')%>%
  flextable::set_table_properties(layout = 'autofit')

IRs_pandemic
```

## Table SX: Consultation rate ratios from interrupted time-series analysis (5 January 2015 to 26 December 2020) for England

```{r echo=FALSE, message = FALSE, quiet=TRUE, warning=FALSE}

# Load packages ----
if (!require('pacman')) install.packages('pacman')
pacman::p_load(tidyverse,lubridate, Hmisc, epitools, data.table, epiR, flextable,
               gtsummary)

# Set working directory ----
setwd("filepath")

# Load data
load(file = "filepath")

RRs_England <- flextable(RRs_England)
RRs_England <- flextable::align(RRs_England, align = 'center', part = 'header')%>%
  flextable::set_table_properties(layout = 'autofit')

RRs_England

```

## Table SX: Consultation rate ratios from interrupted time-series analysis (5 January 2015 to 26 December 2020) in England by age sub-group

```{r echo=FALSE, message = FALSE, quiet=TRUE, warning=FALSE}

# Load packages ----
if (!require('pacman')) install.packages('pacman')
pacman::p_load(tidyverse,lubridate, Hmisc, epitools, data.table, epiR, flextable,
               gtsummary)

# Set working directory ----
setwd("filepath")

# Load data
load(file = "filepath")

RRs_agesubcohort <- flextable(RRs_agesubcohort)
RRs_agesubcohort <- flextable::align(RRs_agesubcohort, align = 'center', part = 'header')%>%
  flextable::set_table_properties(layout = 'autofit')

RRs_agesubcohort

```

## Table SX: Consultation rate ratios from interrupted time-series analysis (5 January 2015 to 26 December 2020) for London

```{r echo=FALSE, message = FALSE, quiet=TRUE, warning=FALSE}

# Load packages ----
if (!require('pacman')) install.packages('pacman')
pacman::p_load(tidyverse,lubridate, Hmisc, epitools, data.table, epiR, flextable,
               gtsummary)

# Set working directory ----
setwd("filepath")

# Load data
load(file = "filepath")

RRs_London <- flextable(RRs_London)
RRs_London <- flextable::align(RRs_London, align = 'center', part = 'header')%>%
  flextable::set_table_properties(layout = 'autofit')

RRs_London

```

## Table SX: Effect modification by ethnicity for the effect of migration on consultation rates before versus during the pandemic (5 January 2015 to 26 December 2020) for England

```{r echo=FALSE, message = FALSE, quiet=TRUE, warning=FALSE}

# Load packages ----
if (!require('pacman')) install.packages('pacman')
pacman::p_load(tidyverse,lubridate, Hmisc, epitools, data.table, epiR, flextable,
               gtsummary)

# Set working directory ----
setwd("filepath")

# Load data
load(file = "filepath")

RRs_England_migstatus_ethnicity <- flextable(RRs_England_migstatus_ethnicity)
RRs_England_migstatus_ethnicity <- flextable::align(RRs_England_migstatus_ethnicity, align = 'center', part = 'header')%>%
  flextable::set_table_properties(layout = 'autofit')

RRs_England_migstatus_ethnicity

```

## Table SX: Consultation rate ratios from interrupted time series sensitivity analysis for England by migration certainty (5 January 2015 to 26 December 2020)

```{r echo=FALSE, message = FALSE, quiet=TRUE, warning=FALSE}

# Load packages ----
if (!require('pacman')) install.packages('pacman')
pacman::p_load(tidyverse,lubridate, Hmisc, epitools, data.table, epiR, flextable,
               gtsummary)

# Set working directory ----
setwd("filepath")

# Load data
load(file = "filepath")

RRs_migcertainty <- flextable(RRs_migcertainty)
RRs_migcertainty <- flextable::align(RRs_migcertainty, align = 'center', part = 'header')%>%
  flextable::set_table_properties(layout = 'autofit')

RRs_migcertainty

```

## Table SX: Consultation rate ratios from interrupted time series sensitivity analysis for England by migration certainty and age sub-group (5 January 2015 to 26 December 2020)

```{r echo=FALSE, message = FALSE, quiet=TRUE, warning=FALSE}

# Load packages ----
if (!require('pacman')) install.packages('pacman')
pacman::p_load(tidyverse,lubridate, Hmisc, epitools, data.table, epiR, flextable,
               gtsummary)

# Set working directory ----
setwd("filepath")

# Load data
load(file = "filepath")

RRs_agesubcohort_migcertainty <- flextable(RRs_agesubcohort_migcertainty)
RRs_agesubcohort_migcertainty <- flextable::align(RRs_agesubcohort_migcertainty, align = 'center', part = 'header')%>%
  flextable::set_table_properties(layout = 'autofit')

RRs_agesubcohort_migcertainty

```

## Table SX: Consultation rate ratios from interrupted time-series analysis (5 January 2015 to 26 December 2020) for England in cohort matched on age and year at joining the CPRD Gold database

```{r echo=FALSE, message = FALSE, quiet=TRUE, warning=FALSE}

# Load packages ----
if (!require('pacman')) install.packages('pacman')
pacman::p_load(tidyverse,lubridate, Hmisc, epitools, data.table, epiR, flextable,
               gtsummary)

# Set working directory ----
setwd("filepath")

# Load data
load(file = "filepath")

RRs_England_SA <- flextable(RRs_England_SA)
RRs_England_SA <- flextable::align(RRs_England_SA, align = 'center', part = 'header')%>%
  flextable::set_table_properties(layout = 'autofit')

RRs_England_SA

```

## Table SX: Effect modification by ethnicity for the effect of migration on pre-pandemic consultation rates

```{r echo=FALSE, message = FALSE, quiet=TRUE}
# Load packages
if (!require('pacman')) install.packages('pacman')
pacman::p_load(flextable, tidyverse)

# Set working directory
setwd("filepath")


load(file="filepath")
load(file="filepath")

# Add  'All' and 'White British' rows to RERI and multiplicative effect dataframe 
int_effects_all_ethnicities <- int_effects_all_ethnicities %>%
  mutate(across(where(is.numeric), ~ round(.,2))) %>%
  mutate(RERI_CI = paste0(RERI, ' (', RERI_lower_CI, '-', RERI_upper_CI, ')'),
         Multiplicative_CI = paste0(multiplicative_effect, ' (', mult_lower_CI, '-', mult_upper_CI, ')'))


all <- data.frame(ethnicity = 'All', RERI_CI = NA, Multiplicative_CI = NA)
white_british <- data.frame(ethnicity = 'White British', RERI_CI = NA, Multiplicative_CI = NA)

int_effects_all_ethnicities <- bind_rows(white_british, int_effects_all_ethnicities, all) %>%
  dplyr::select(Multiplicative_CI, RERI_CI)

# Bind columns
ethnicity_table <- bind_cols(ethnicity_table, int_effects_all_ethnicities)

# Create table
ethnicity_table_ft <- flextable(ethnicity_table) %>%
  set_table_properties(layout = 'autofit')
ethnicity_table_ft

```


## Table SX: Effect modification by ethnicity (18 categories) for the effect of migration on pre-pandemic consultation rates

```{r echo=FALSE, message = FALSE, quiet=TRUE}
# Load packages
if (!require('pacman')) install.packages('pacman')
pacman::p_load(flextable, tidyverse)

# Set working directory
setwd("filepath")


load(file="filepath")
load(file="filepath")

# Add  'All' and 'White British' rows to RERI and multiplicative effect dataframe 
int_effects_all_ethnicat18 <- int_effects_all_ethnicat18 %>%
  mutate(across(where(is.numeric), ~ round(.,2))) %>%
  mutate(RERI_CI = paste0(RERI, ' (', RERI_lower_CI, '-', RERI_upper_CI, ')'),
         Multiplicative_CI = paste0(multiplicative_effect, ' (', mult_lower_CI, '-', mult_upper_CI, ')'))

white_british <- data.frame(ethnicity = 'White British', RERI_CI = NA, Multiplicative_CI = NA)

int_effects_all_ethnicat18 <- bind_rows(white_british, int_effects_all_ethnicat18) %>%
  dplyr::select(Multiplicative_CI, RERI_CI)

# Bind columns
ethnicity_table <- bind_cols(ethnicity_table, int_effects_all_ethnicat18)

# Create table
ethnicity_table_ft <- flextable(ethnicity_table) %>%
  set_table_properties(layout = 'autofit')
ethnicity_table_ft

```

## Table SX: Effect modification by ethnicity (18 category) for the effect of migration on consultation rates before versus during the pandemic (5 January 2015 to 26 December 2020) for England

```{r echo=FALSE, message = FALSE, quiet=TRUE, warning=FALSE}

# Load packages ----
if (!require('pacman')) install.packages('pacman')
pacman::p_load(tidyverse,lubridate, Hmisc, epitools, data.table, epiR, flextable,
               gtsummary)

# Set working directory ----
setwd("filepath")

# Load data
load(file = "filepath")

RRs_England_migstatus_ethnicity18cat <- flextable(RRs_England_migstatus_ethnicity18cat)
RRs_England_migstatus_ethnicity18cat <- flextable::align(RRs_England_migstatus_ethnicity18cat, align = 'center', part = 'header')%>%
  flextable::set_table_properties(layout = 'autofit')

RRs_England_migstatus_ethnicity18cat

```

## Table SX: Consultation rate ratios from interrupted time-series analysis (5 January 2015 to 26 December 2020) for England in cohort matched on age at study start and gender only (SA2)

```{r echo=FALSE, message = FALSE, quiet=TRUE, warning=FALSE}

# Load packages ----
if (!require('pacman')) install.packages('pacman')
pacman::p_load(tidyverse,lubridate, Hmisc, epitools, data.table, epiR, flextable,
               gtsummary)

# Set working directory ----
setwd("filepath")

# Load data
load(file = "filepath")

RRs_England_SA2 <- flextable(RRs_England_SA2)
RRs_England_SA2 <- flextable::align(RRs_England_SA2, align = 'center', part = 'header')%>%
  flextable::set_table_properties(layout = 'autofit')

RRs_England_SA2

```

## Table SX: Consultation rate ratios from interrupted time-series analysis (5 January 2015 to 26 December 2020) for England in cohort matched on age at study start, practice region and gender only (SA3)

```{r echo=FALSE, message = FALSE, quiet=TRUE, warning=FALSE}

# Load packages ----
if (!require('pacman')) install.packages('pacman')
pacman::p_load(tidyverse,lubridate, Hmisc, epitools, data.table, epiR, flextable,
               gtsummary)

# Set working directory ----
setwd("filepath")

# Load data
load(file = "filepath")

RRs_England_SA3 <- flextable(RRs_England_SA3)
RRs_England_SA3 <- flextable::align(RRs_England_SA3, align = 'center', part = 'header')%>%
  flextable::set_table_properties(layout = 'autofit')

RRs_England_SA3

```

